---
output: 
  pdf_document:
    latex_engine: pdflatex
    template: svm-latex-cv.tex
geometry: margin=1in

title: "D. Palleschi - Curriculum Vitae"
author: "Daniela Palleschi"

jobtitle: "Scientific support (Referentin) for statistics and data management"
address: "Leibniz-Zentrum Allgemeine Sprachwissenschaft (ZAS; Leibniz-Centre General Linguistics)"
fontawesome: yes
email: palleschi@leibniz-zas.de
# github: daniela-palleschi
# twitter: 
#osf: "Enter 5 digit osf string here"
# phone: "+353 1 408 4800"
web: daniela-palleschi.github.io
updated: TRUE
rdateformat: "`r format(Sys.time(), '%d %b %Y')`"

keywords: R Markdown, academic CV, template

fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 11pt
linkcolor: red
urlcolor: black
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = F,
                      message = F)
```


# Academic appointments

```{r}
pacman::p_load(tidyverse, gt, knitr, kableExtra)
```

```{r}
current_job <-
  tribble(
  ~"Year", ~"Title",
  # ZAS job
  "09.2024 - present","\\textbf{Scientific support for data science and data management} (Referentin)",
    "", "Leibniz-Zentrum Allgemeine Sprachwissenschaft (ZAS)",
)
```


```{r}
past_jobs <-
  tribble(
  ~"Year", ~"Title",
  # Stats job
  "02.2023 - 08.2024","\\textbf{Statistics consultant and Scientific staff member} (wiss. Mitarbeiterin)",
    "", "Humboldt-Universität zu Berlin, Institute for German Langauge and Linguistics",
  # DFG job
  "12.2019 - 01.2023","\\textbf{Research Fellow} (wiss. Mitarbeiterin)",
    "", "Humboldt-Universität zu Berlin, Institute for German Langauge and Linguistics",
    "", "DFG, grant KN 897/9-1: ‘Effects of lifetime and fact knowledge in language
  comprehension’"
)
```


```{r}
rbind(current_job, past_jobs) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
        bottomrule = '',
        toprule = '',
        midrule = '',
    linesep = "") 

```


# Education

```{r}
phd <-
  tribble(
  ~"Year", ~"Title",
  "2024","\\textbf{Doctorate in Psycholinguistics} (dr. phil); submitted 2023",
    "", "Humboldt-Universität zu Berlin, Institute for German Langauge and Linguistics",
    "", "Dissertation title: \\textit{Processing the Perfect Lifetime Effect: The role of}
  \\textit{referent-lifetime knowledge in the processing of temporal relations}",
  "", ""
)

mind_brain <-
  tribble(
  ~"Year", ~"Title",
  "2017 - 2024","\\textbf{Doctoral student} of the Berlin School of Mind and Brain",
    "", "Humboldt-Universität zu Berlin",
  "", ""
)

ecn <-
  tribble(
  ~"Year", ~"Title",
  "2017-2024","\\textbf{Doctoral fellow} of the Einstein Center for Neurosciences Berlin",
    "", "Charité - Universitätsmedizin Berlin",
  "", ""
)
```


```{r}
msc <-
  tribble(
  ~"Year", ~"Title",
  "2017","\\textbf{M.Sc. in Clinical Linguistics} (Erasmus Mundus joint Master Degree)",
    "", "University of Eastern Finland, University of Potsdam, University of Groningen (NL)"
)

ma <-
  tribble(
  ~"Year", ~"Title",
  "2017","\\textbf{M.A. in Clinical Linguistics}",
    "", "University of Finland"
)


ba <-
  tribble(
  ~"Year", ~"Title",
  "2012","\\textbf{B.A. Honours Specialist in Linguistics}",
    "", "University of Toronto"
)

```

```{r}
rbind(phd, ecn, mind_brain,
      msc, ma, ba) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
    linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 
```

# Awards and Fellowships

```{r}
ecn <-
  tribble(
  ~"Year", ~"Title",
  "2017-2024","\\textbf{Doctoral scholarship} of the Einstein Center for Neurosciences Berlin",
    "", "\\textit{Charité - Universitätsmedizin Berlin}"
)

```

```{r}
rbind(ecn) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
    linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 
```

# Teaching Experience

```{r}
sol <-
    tribble(
    ~"Year", ~"Course",
    "August 2024", "\\textbf{Open Science Practices for Linguistic Research: Reproducible Analyses in R}",
        "", "Web book: \\href{https://daniela-palleschi.github.io/SSOL24-reproducibility-workshop/}{\\textit{https://daniela-palleschi.github.io/SSOL24-reproducibility-workshop/}}",
    "", "Summer School of Linguistics, Budweis, Czechia (4-day workshop)",
    "", ""
  ) # https://daniela-palleschi.github.io/SSOL24-reproducibility-workshop/

open_sci <- 
  tribble(
    ~"Year", ~"Course",
    "2024", "\\textbf{Open Science Practices: Implementing a Reproducible Analysis Workflow},",
    "", "Web book: \\href{https://daniela-palleschi.github.io/r4repro_SoSe2024/}{\\textit{https://daniela-palleschi.github.io/r4repro\\_SoSe2024/}}",
    "", "M.A. course, Institut für deutsche Sprache und Linguistik,",
    "", "Humboldt-Universität zu Berlin",
    "", ""
  )

reg_ling <- 
  tribble(
    ~"Year", ~"Course",
    "2023 - 2024", "\\textbf{Regression for Linguists}",
    "", "Web book: \\href{https://daniela-palleschi.github.io/reg4ling/}{\\textit{https://daniela-palleschi.github.io/reg4ling/}}",
    "", "M.A. course, Institut für deutsche Sprache und Linguistik,",
    "", "Humboldt-Universität zu Berlin",
    "", ""
  )

repro_et <- 
  tribble(
    ~"Year", ~"Course",
    "2023", "\\textbf{Reproducible analysis reports with eye-tracking reading time data}",
    "", "Web book: \\href{https://daniela-palleschi.github.io/repo-eda/}{\\textit{https://daniela-palleschi.github.io/repo-eda/}}",
    "", "M.A. course, Institut für deutsche Sprache und Linguistik,",
    "", "Humboldt-Universität zu Berlin",
    "", ""
  )

r_ling <- 
  tribble(
    ~"Year", ~"Course",
    "2023 - 2024", "\\textbf{Angewandte Datenverarbeitung und Visualisierung}",
    "", "Web book: \\href{https://daniela-palleschi.github.io/r4ling/}{\\textit{https://daniela-palleschi.github.io/r4ling/}}",
    "", "B.A. course, Institut für deutsche Sprache und Linguistik,",
    "", "Humboldt-Universität zu Berlin",
    "", ""
  )

intro_stats <-
    tribble(
    ~"Year", ~"Course",
    "2019 - 2020", "\\textbf{Introduction to Statistics with R and RStudio}",
    "", "B.A. course, Institut für deutsche Sprache und Linguistik,",
    "", "Humboldt-Universität zu Berlin",
    "", ""
  )

lang_brain <-
    tribble(
    ~"Year", ~"Course",
    "2019 - 2020", "\\textbf{Language and the Brain} (tutorial)",
    "", "M.A. course for Berlin School of Mind and Brain, Humboldt-Universität zu Berlin",
    "", "Accompanied lectures from Prof. Pia Knoeferle and Prof. Friedemann Pulvermüller"
  )

pcibex <-
      tribble(
    ~"Year", ~"Course",
    "2020", "\\textbf{Introduction to Ibex and PennController: Internet-based experiments} (workshop)
    Institut für deutsche Sprache und Linguistik, Humboldt-Universität zu Berlin",
    "", ""
  )
  
```

```{r}
rbind(
      sol
      # reg_ling
      # r_ling,
      # repro_et,
      # pcibex,
      # intro_stats,
      # lang_brain
      ) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
        linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 

rbind(open_sci,
      reg_ling,
      r_ling,
      repro_et,
      pcibex,
      intro_stats,
      lang_brain) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
        linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 
```

# Non-academic experience

```{r}
linguarama <-
      tribble(
    ~"Year", ~"Experience",
    "2012-2017", "\\textbf{Teacher of English as a Second Language} (adults and children)",
    "", "Marcus Evans Linguarama, Berlin, Germany"
  )

tesol <-
      tribble(
    ~"Year", ~"Experience",
    "2012", "\\textbf{TESOL Certification} (Teacher of English to Speakers of Other Languages)",
    "", "SOL International School of Language, Toronto, Canada"
  )
```

```{r}
rbind(linguarama,
      tesol) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
        linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 
```

# Workshops, summer schools, journal clubs (attendance)

## Data Analyses

```{r}

random_forests <-
      tribble(
    ~"Year", ~"Experience",
    "2023 - ", "\\textbf{The Practical Application of Decision Tree-Based AI Models} (workshop)",
    "", "Leibniz-Centre General Linguistics (ZAS), Berlin"
  )

cluster_analysis <-
      tribble(
    ~"Year", ~"Experience",
    "2023 - ", "\\textbf{Cluster analysis on f0 contours: advantages, pitfalls, challenges} (online workshop)",
    "", "LingLabs, University of Konstanz"
  )


bayes_zas <-
      tribble(
    ~"Year", ~"Experience",
    "2023 - ", "\\textbf{Bayesian group meet-up} (group member)",
    "", "regular meeting with members of the Leibniz-Centre General Linguistics (ZAS)"
  )

bayes_hpi <-
      tribble(
    ~"Year", ~"Experience",
    "2023 - ", "\\textbf{Introduction to Bayesian Data Analysis} (course)",
    "", "openHPI online course (instructor: Prof. Shravan Vasishth)"
  )

bayes_konstanz <-
      tribble(
    ~"Year", ~"Experience",
    "2022", "\\textbf{Intro to Bayesian Analyses for Speech and Language Scientists}, (workshop)",
    "", "University of Konstanz, Germany"
  )

bayes_smlp <-
      tribble(
    ~"Year", ~"Experience",
    "2022", "\\textbf{Introduction to Bayesian Analysis} (course)",
    "", "Summer School in Statistical Methods for Linguistics and Psychology (SMLP)",
    "", "Universität Potsdam,Germany"
  )

julia_smlp <-
      tribble(
    ~"Year", ~"Experience",
    "2021", "\\textbf{Advanced methods in frequentist statistics with Julia} (course)",
    "", "Summer School in Statistical Methods for Linguistics and Psychology (SMLP)",
    "", "Universität Potsdam, Germany"
  )

freq_smlp <-
      tribble(
    ~"Year", ~"Experience",
    "2022", "\\textbf{Foundational methods in frequentist statistics} (course)",
    "", "Summer School in Statistical Methods for Linguistics and Psychology (SMLP)",
    "", "Universität Potsdam,Germany"
  )

gamms <-
      tribble(
    ~"Year", ~"Experience",
    "2022", "\\textbf{Generalised Additive Modelling in Statistics} (workshop)",
    "", "Leibniz-Zentrum Allgemeine Sprachwissenschaft(ZAS Berlin), Germany"
  )
```



```{r}
rbind(
      random_forests,
      cluster_analysis,
      bayes_zas,
      bayes_hpi
      # bayes_konstanz
      # bayes_smlp,
      # gamms
      # julia_smlp
      ) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
        linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 
```

```{r}
rbind(
      # bayes_zas,
      # bayes_hpi,
      bayes_konstanz,
      bayes_smlp,
      gamms,
      julia_smlp,
      freq_smlp) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
        linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 
```

## Methods and MetaScience


```{r}

ag_git <-
      tribble(
    ~"Year", ~"Experience",
    "2024 - ", "\\textbf{Git Arbeitsgruppe} (member)",
    "", "Interdisziplinäres Zentrum für Digitalität und digitale Methoden am Campus Mitte",
    "", "Humboldt-Universität zu Berlin"
  )

coding_club <-
      tribble(
    ~"Year", ~"Experience",
    "2022", "\\textbf{Coding Club::Creating an R Package} (online workshop)",
    "", "Creating an R package to share code and data from a research project"
  )

git_collab <-
      tribble(
    ~"Year", ~"Experience",
    "2022", "\\textbf{Git Collaborative} (workshop)",
    "", "Max Planck Institute for Psycholinguistics"
  )

git_basics <-
      tribble(
    ~"Year", ~"Experience",
    "2022", "\\textbf{Git Basics} (workshop)",
    "", "Max Planck Institute for Psycholinguistics"
  )

tidyverse <-
      tribble(
    ~"Year", ~"Experience",
    "2021", "\\textbf{Data wrangling and reproducible reports with tidyverse and R-markdown} (workshop)",
    "", "Universität Freiburg"
  )

```

```{r}
rbind(ag_git,
      coding_club,
      git_collab,
      git_basics,
      tidyverse) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
        linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 
```

# Organisation and Service

```{r}
friday_primes <-
      tribble(
    ~"Year", ~"Experience",
    "2020 - ", "\\textbf{Friday Primes} (co-founder and -organiser)",
    "", "monthly meet-up for Early Career Researchers in psycholinguistics in Berlin/Brandenburg"
  )

eslp_attlis <-
      tribble(
    ~"Year", ~"Experience",
    "2019", "\\textbf{Embodied and Situated Language Processing and AttLis} (conference co-organiser)",
    "", "Humboldt-Universität zu Berlin, Germany"
  )

amlap <-
      tribble(
    ~"Year", ~"Experience",
    "2019", "\\textbf{Architecture and Mechanisms for Language Processing} (conference on-site organisation)",
    "", "Berlin, Germany"
  )
```


```{r}
rbind(friday_primes,
      eslp_attlis,
      amlap) %>%  
  mutate_all(linebreak) |> 
  knitr::kable(
    col.names = NULL,
    format = "latex", escape = F,
        booktabs = T,
        linesep = "",
        bottomrule = '',
        toprule = '',
        midrule = '') 
```

# Technical skills

Eye-tracking (EyeLink 1000, Experiment Builder, EyeLink DataViewer)\hfill\break
Internet-based experiments (PCIbex, Prolific, ClickWorker)\hfill\break
EEG data collection (BrainProducts)\hfill\break
R and RStudio (data wrangling, analysis, visualisation)\hfill\break
Technical writing/Dynamic reports (Quarto, RMarkdown, LaTeX)\hfill\break
Version control (Git, GitHub, GitLab)

# Memberships

*Cognitive Science Society* \hfill 2020 - present\break
*Berlin School of Mind and Brain*, Humboldt-Universität zu Berlin \hfill 2018 - present\break
*Einstein Center for Neurosciences Berlin*, Charité - Universitätsmedizin Berlin \hfill 2017 - present\break

# Publications

## Peer-reviewed Conference Proceedings

\begingroup
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}

**Palleschi, D.**, Knoeferle, P. (2022). “Activation of biographical information via picture of cultural figures: an eye-tracking during reading study” *Proceedings of the 42nd
Annual Meeting of the Cognitive Science Society.* Toronto, Canada: Cognitive Science Society

**Palleschi, D.**, Ronderos, C.R., Knoeferle, P. (2020). “Effects of linguistic context and world knowledge on the processing of tense and aspect: evidence from eye-tracking” *Proceedings of the 42nd
Annual Meeting of the Cognitive Science Society.* Toronto, Canada: Cognitive Science Society

\endgroup
## Under review

**Palleschi, D.**, Ronderos, C.R., Knoeferle, P. (under review) “Living in the present - how referent lifetime influences processing of past, present (perfect), and future tenses”

## Selected Conference Presentations

*Experimental Pragmatics Conference (XPrag)*, Pavia, Italy \hfill 2022 \break
**Palleschi, D.**, Ronderos, C.R., Knoeferle, P. "Processing the Perfect Lifetime Effect: the role of lifetime information source." (poster)

*Architectures and Mechanisms of Language Processing*, University of York, UK \hfill 2022 \break
**Palleschi, D.**, Knoeferle, P. "Availability of speaker-specific lifetime and biographical knowledge during comprehension: evidence from eye-tracking during reading." (poster)

*Experiments in Linguistic Meaning (ELM)*, University of Pennsylvania, USA \hfill 2022 \break
**Palleschi, D.**, Ronderos, C.R., Knoeferle, P. "Effects of referent lifetime knowledge on processing of verb morphology." (poster)

*Processing Tense Workshop*, Tübingen,  \hfill 2019\break
**Palleschi, D.**, Ronderos, C.R., Knoeferle, P. "Processing the Present Perfect Lifetime Effect: an eye-tracking during reading study on the integration of context, tense, and aspect" (talk)

# Mentoring and training

Mentored Master's Thesis on world knowledge effects in tense processing (Aliona Petrenco);\hfill \break
Hired, trained, and managed three research assistants (Studentische und wissenschaftliche Hilfskraft); \hfill \break
Training of student interns in data collection (eye-tracking and EEG)

# Language competences

English (native)\hfill\break
German (Intermediate)\hfill\break

# References

Available upon request
\vfill
